CannonRV: Measuring radial velocities with a data-driven spectral model

### 2017-01-15 paper/ms.tex
Demonstrate our normalization method works

@@

The radial velocity is related to the pixels. We can obtain the velocity shift by calculating the centroid shift.

@@

But if 2b<a+c, which means the magnitude of the spectrum moves one pixel left or right is big, the approximation will expire because the influence of the pixels two pixel left or right can't be ignored. When this happen, we will use five parameters, which are:

@@

In figure 16, we plot the continuum-normalized fluxes of all visits for the first star in figure 8. There are 9 individual visits. We can see that the absolute value of the flux for each visit is similar to each other, which means our normalization works.

@@

\centerline{Fig.17 Comparison of each visit for the first star in figure 8.}
\bigskip

@@

>>>>

\usepackage{amsmath}

@@

The radial velocity is related to the pixels. We can obtain the velocity shift by calculating the centroid shift. The centroid in pixel can be expressed as:

@@

But if 2b<a+c, which means the magnitude of the spectrum moves one pixel left or right is big, the approximation will expire because the influence of the pixels two pixels left or right can't be ignored. When this happens, we will use five parameters, which are:
$a_1$, $a_2$, $a_3$, $a_4$, $a_5$. Now the optimized spectrum is:

\begin{equation}
y_{j,n}^{opt}=a_1\cdot y_{j+2,n}^{inf}+a_2\cdot y_{j+1,n}^{inf}+a_3\cdot y_{j,n}^{inf}+a_4\cdot y_{j-1,n}^{inf}+a_5\cdot y_{j-2,n}^{inf}
\end{equation}
This means we move the inferred spectrum two pixels left, one pixel left, zero pixel, one pixel right and two pixels right and generate five new spectrums. The parameters for them are $a_1$, $a_2$, $a_3$, $a_4$, $a_5$. We only use five parameters to calculate the radial velocity shift when $2b<a+c$, where the influence of the spectrum moves two pixels left and right can't be ignore.

So the velocity shift is

\begin{equation}
RV_{shift} = v_{pixel} \cdot {{c-a}\over{a+b+c}}\qquad2b>a+c
\end{equation}

\begin{equation}
RV_{shift} = v_{pixel} \cdot {{2a_5 +a_4 - a_2 - 2a_1}\over{a_1+a_2+a_3+a_4+a_5}}\qquad2b<a+c     
\end{equation}

We will plot the histogram for the five parameters in our experiment.

@@

In figure 17 and 18, we plot the continuum-normalized fluxes of all visits for the first star in figure 8. There are 6 individual visits and 2 combined spectrums. So in figure 17 and 18, there are 8 fluxes. The bottom two are the combined spectrum and the other 6 are individual visits. We can see that the absolute value of the flux for each visit is similar to each other, which means our normalization works.

@@

\centerline{Fig.17 Comparison of each visit for the first star in figure 8.}
\centerline{The bottom two are the combined spectrum and the other 6 are individual visits. The red dots are continuum pixels }
\bigskip

\begin{center}
\includegraphics[width=170mm]{figure_18.png}
\end{center}

\centerline{Fig.18 Comparison of each visit for the first star in figure 8.}
\centerline{The bottom two are the combined spectrum and the other 6 are individual visits. The red dots are continuum pixels }
\bigskip

@@

\begin{center}
\includegraphics[width=170mm]{d_figure_7.png}
\end{center}

\centerline{Diagnostic Fig.7 Radial velocity shifts}
\centerline{ $v_3$ is the RV shift obtained from a, b and c. $v_5$ is from the five parameters. $v$ is from a, b and c if $2b>a+c$ and $v$ = $v_5$ if $2b<a+c$}
\bigskip
